---
title: "chapter 4"
author: "Alicia Sillers"
date: "2022-09-12"
output: 
  html_document:
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Quiz

1. What is the result of subsetting a vector with positive integers, negative integers, a logical vector, or a character vector?
My Answer: I'm not sure what this means.
Textbook Answer: Positive integers select elements at specific positions, negative integers drop elements; logical vectors keep elements at positions corresponding to TRUE; character vectors select elements with matching names.

2. What’s the difference between [, [[, and $ when applied to a list?
My Answer: I know $ is used to select an element by name. I'm not sure how the others compare.
Textbook Answer: [ selects sub-lists: it always returns a list. If you use it with a single positive integer, it returns a list of length one. [[ selects an element within a list. $ is a convenient shorthand: x$y is equivalent to x[["y"]].

3. When should you use drop = FALSE?
My Answer: I don't know. 
Textbook Answer: Use drop = FALSE if you are subsetting a matrix, array, or data frame and you want to preserve the original dimensions. You should almost always use it when subsetting inside a function.

4. If x is a matrix, what does x[] <- 0 do? How is it different from x <- 0?
My Answer: I believe x[] <- 0 would empty the matrix whereas x <- 0 would make x represent the number 0 rather than a matrix. 
Textbook Answer: If x is a matrix, x[] <- 0 will replace every element with 0, keeping the same number of rows and columns. In contrast, x <- 0 completely replaces the matrix with the value 0.

5. How can you use a named vector to relabel categorical variables?
My Answer: I don't know.
Textbook Answer: A named character vector can act as a simple lookup table: c(x = 1, y = 2, z = 3)[c("y", "z", "x")]

# 4.2.6 Exercises

1. Fix each of the following common data frame subsetting errors:
mtcars[mtcars$cyl = 4, ]
mtcars[-1:4, ]
mtcars[mtcars$cyl <= 5]
mtcars[mtcars$cyl == 4 | 6, ]

Answer:
```{r}
mtcars[mtcars$cyl == 4, ]
mtcars[-1:-4, ]
mtcars[mtcars$cyl <= 5, ]
mtcars[mtcars$cyl == 4 | 6, ] #not sure what the problem is here
```

2. Why does the following code yield five missing values? (Hint: why is it different from x[NA_real_]?)
```{r}
x <- 1:5
x[NA]
#> [1] NA NA NA NA NA
```
Answer: A missing value in the input always yields a missing value in the output.

3. What does upper.tri() return? How does subsetting a matrix with it work? Do we need any additional subsetting rules to describe its behaviour?
```{r}
x <- outer(1:5, 1:5, FUN = "*")
x[upper.tri(x)]
```
Answer: upper.tri() returns a matrix of logical values with TRUE as the value of every position in the upper triangle of the matrix and FALSE for everything else. I think x[upper.tri(x)] returns the values that upper.tri would return as TRUE, meaning that it returns the values in the upper triangle of the matrix. 

4. Why does mtcars[1:20] return an error? How does it differ from the similar mtcars[1:20, ]?
Answer: It returns an error because mtcars is a dataset, so to subset from it there needs to be an indication both of which rows to select and which columns to select. mtcars[1:20, ] differs because the comma indicated that 1:20 refers to rows and that whatever is after the comma refers to columns. Since there is no value in this case, it refers to all columns. 

5. Implement your own function that extracts the diagonal entries from a matrix (it should behave like diag(x) where x is a matrix).
Answer:
```{r}
fdiagonal <- function(m){
  diag(m)
}

fdiagonal(x)
```

6. What does df[is.na(df)] <- 0 do? How does it work?
Answer: I think it would replace all values of 0 with NA.

# 4.3.5 Exercises

1. Brainstorm as many ways as possible to extract the third value from the cyl variable in the mtcars dataset.
Answer:
```{r}
mtcars$cyl[[3]]
mtcars[[3, 'cyl']]
```

2. Given a linear model, e.g., mod <- lm(mpg ~ wt, data = mtcars), extract the residual degrees of freedom. Then extract the R squared from the model summary (summary(mod))
Answer:
```{r}
mod <- lm(mpg ~ wt, data = mtcars)
mod$df.residual
summary(mod)[[8]]
```

# 4.5.9 Exercises

1. How would you randomly permute the columns of a data frame? (This is an important technique in random forests.) Can you simultaneously permute the rows and columns in one step?
Answer: df[, sample(ncol(df))]. You can permute rows and columns in one step 

2. How would you select a random sample of m rows from a data frame? What if the sample had to be contiguous (i.e., with an initial row, a final row, and every row in between)?
Answer: ??? use sample() to select random rows, but not sure how to generate a random number or rows or how to make them contiguous. 

3. How could you put the columns in a data frame in alphabetical order?
Answer: You could apply order() to the column names: df[, order(colnames(df))]


